Shrinking Characteristics of Precision Matrix Estimators: An Illustration via Regression

### 2019-01-09 01-intro.Rmd
testing new travis
new travis 2
new travis 3
new travis 4
new travis 5
Deploy MGallow/oral_manuscript to github.com/MGallow/oral_manuscript.git:master
new travis 7, turned off keep-history
bug fix, changed allow empty commit
updated material with new vignettes
restructed manuscript

This is the introduction for Matt's oral manuscript.

>>>>

In many statistical applications, estimating the covariance for a set of random variables is a critical task. The covariance is useful because it characterizes the *relationship* between variables. For instance, suppose we have three variables $X, Y, \mbox{ and } Z$ and their covariance matrix is of the form

\[ \Sigma_{xyz} = \begin{pmatrix}
1 & 0 & 0.5 \\ 
0 & 1 & 0 \\ 
0.5 & 0 & 1
\end{pmatrix} \]

We can gather valuable information from this matrix. First of all, we know that each of the variables has an equal variance of 1. Second,  we know that variables $X$ and $Y$ are likely independent because the covariance between the two is equal to 0. This implies that any information in $X$ is useless in trying to gather information about $Y$. Lastly, we know that variables $X$ and $Z$ are moderately, positively correlated because their covariance is 0.5.

Unfortunately, estimating $\Sigma$ well is often computationally expensive and, in a few settings, extremely challenging. For this reason, emphasis in the literature and elsewhere has been placed on estimating the inverse of $\Sigma$ which we like to denote as $\Omega \equiv \Sigma^{-1}$.

- Why do we care?

- What is SCPME?

- Guide

- Model and notation
